\documentclass[11pt,a4paper]{article}

% --- Packages -----------------------------------------------------------
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{lmodern}
\usepackage[top=1.6cm,bottom=1.6cm,left=1.9cm,right=1.9cm]{geometry}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}

% --- Layout tweaks ------------------------------------------------------
\titlespacing*{\section}{0pt}{0.45em}{0.1em}
\titleformat{\section}{\normalfont\normalsize\bfseries}{}{0pt}{}
\setlist{nosep,leftmargin=1.2em,topsep=1pt,parsep=0pt,itemsep=1pt}
\setlength{\parskip}{0.25em}
\pagenumbering{gobble}

\begin{document}

% --- Title block --------------------------------------------------------
\begin{center}
{\Large\bfseries The Simplification Trade-off}\\[0.15em]
{\normalsize Comparing ML, DL, SLM and LLM Approaches to Text Simplification}\\[0.4em]
{\small Alhasan Ramadan \quad\textbar\quad Samuel Freundel \quad\textbar\quad Kanwal Kahn \quad\textbar\quad Simon Volbon}\\[0.15em]
{\footnotesize Universit\"at Ulm \textbar{} Natural Language Processing and Neural Language Models \textbar{} Prof.\ Dr.\ Yousef Younes \textbar{} \today}
\end{center}
\vspace{-0.1em}
\hrule
\vspace{0.3em}

\section*{Motivation}

\section*{Research Questions}
Research on text simplification(TS) has become a significant topic in the field of Natural Language Processing(NLP) due to its use in education, medicine, legal administration, among others. The goal of text simplification is to break down complex texts into a simpler, more readable form while trying to preserve the necessary information that the original complex text conveys. However, it is often difficult to preserve the same informational value and/or the original meaning in the simplified version, leading to a trade-off between the simplicity of the text and the meaning and information that the text once contained. Over years of research, there have been various approaches to text simplification. Early methods were often based on Rules to simplify language, such as replacing difficult words with simpler synonyms or splitting long sentences into multiple shorter ones. Later deep learning approaches were used because they were better at learning the often complex patterns used in our languages. With the recent improvements in small language models (SLMs) and large language models(LLMs), there have been advancements in the topic of simplification as well. The aim  of the paper is to research how text simplification affects the trade-off between readability and information preservation across Machine Learning, Deep Learning, Small Language Models, and Large Language Models approaches.

\section{Theoretical Framework \& Literature}
Previous work on text simplification commonly treats the task as a monolingual text-to-text rewriting problem,
where a complex input sentence is transformed into a simpler output sentence. Earlier approaches include
rule-based syntactic simplification, lexical simplification through simpler word substitutions, statistical machine
translation methods, and neural sequence-to-sequence models. DRESS is a relevant example of a neural approach,
using an encoder-decoder architecture combined with reinforcement learning to optimize simplification-specific
objectives such as simplicity, fluency, and meaning preservation. More recent evaluation resources such as
ASSET emphasize that simplification can involve multiple rewrite operations, including sentence splitting,
paraphrasing, reordering, deletion, and compression. Therefore, our methodological basis should not only
compare surface-level readability, but also consider whether the simplified output preserves the factual and
semantic content of the original text.
Relevant metrics include SARI for simplification edits, BLEU and ROUGE for reference overlap, Flesch-Kincaid
for readability, semantic similarity for meaning preservation, and entity or number preservation for factual
consistency.

\section*{Methodology}
Building on these foundations, our methodology adopts a comparative experimental design across four model families representing distinct paradigms: a classical statistical machine-learning baseline, a deep-learning sequence-to-sequence model based on the DRESS architecture, a fine-tuned small language model and a large language model evaluated in a zero-shot prompting setting. The smaller models are trained or fine-tuned on the WikiLarge corpus of aligned English and Simple English Wikipedia sentence pairs, while all four systems are tested against the ASSET benchmark to ensure comparability with prior work. To address the three sub-questions, we measure readability using Flesch-Kincaid and SARI and quantify semantic preservation through BERTScore similarity and a downstream question-answering probe on SQuAD passages. Regarding the question-answering probe, the accuracy delta between answers derived from original and simplified texts serves as a proxy for information loss. To identify which information types are most affected by simplification, an additional error analysis aligns named entities, numerical facts and discourse relations across source and output pairs. The combined results are aggregated into per-model readability-preservation trade-off curves, enabling a structured comparison across paradigms.
\section*{}


\section*{Work Plan \& Expected Outcomes}


\end{document}
